Red Wine by Fillarry Susanto
========================================================
  
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(plyr)
library(GGally)
library(gridExtra)
library(RColorBrewer)
library(knitr)
library(corrplot)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
#getwd()
#setwd('C:/Users/aduuh/Documents/Python Scripts/udda/eda')

redWine <- read.csv('wineQualityReds.csv')
```

This report explores a dataset containing the chemical content of 1599 red wines
and the resulting evaluation of their tastes according to wine experts, scaled
from 0 to 10.

# Univariate Plots Section


```{r echo=FALSE}
dim(redWine)
```

```{r echo=FALSE}
str(redWine)
```

```{r echo=FALSE}
summary(redWine)
```

The Red Wine data ste contains 1599 observations with 13 variables. There are 
no sweet red wine as max of residual sugar is 15.5 g/L where it is considered
sweet only when sugar > 45 g/L.


```{r echo=FALSE}
#create function to plot histogram of one variable
create_hist <- function(variable, binwidth = 0.01) {
  return(ggplot(aes(variable), data = redWine) + 
           geom_histogram(binwidth = binwidth))
  }
```

```{r echo=FALSE}
ggplot(aes(quality), data=redWine) + geom_bar()
```

The quality of red wine seems to have a normal distribution with a maximum 
number at quality=5 and they have discrete values. It seeems most wine are just 
average while there are a few that is really bad and a few that are really good.
None of them is better than 8 though (I guess no wine is perfect). Let us now 
look at the different distribution of the chemical content, starting with the 
different acids.

```{r echo=FALSE}
grid.arrange( create_hist(redWine$fixed.acidity, 0.1) +
  xlab('Fixed Acidity'), 
create_hist(redWine$volatile.acidity, 0.01) +
  xlab('Volate Acidity'), 
create_hist(redWine$citric.acid, 0.01) +
  xlab('Citric Acid'))
```

The fixed, volatile and citric acid concentrations follow a slightly positively
skewed distribution with a long tail. Also, there are a lot of the wine that do
not have any citric acid content in it (around 10% does not have citric acid.
Citric acid is known to add fresh flavor to the wine. I wonder if having the 
freshness increases the quality of wine.

```{r echo=FALSE}
summary(redWine['citric.acid'] == 0)
```

Volatile acid consists of mainly acetic acid which can lead to unpleasant 
vinegary taste, I wonder what is the threshold amount of volatile acid where 
the quality of wine starts to drop. Now, let's look at the statistics of fixed
acidity, volatile acidity and citric acid in that order shown below:

```{r echo=FALSE}
summary(redWine$fixed.acidity)
summary(redWine$volatile.acidity)
summary(redWine$citric.acid)
```

Since the distribution is long tailed, the max values are really high, greater
than twice of the 3rd quartile. But I decided to keep all the outliers because
I believe that this is very possible concentration for red wines as they come
from different grapes and processed differently.
 

Next thing to look at is the sulfur content.

```{r echo=FALSE, Univariate_Plots}
grid.arrange(create_hist(redWine$free.sulfur.dioxide, 1) +
  xlab('Free Sulfur Dioxide'), 
create_hist(redWine$total.sulfur.dioxide, 2) +
  xlab('Total Sulfur Dioxide'), 
create_hist(redWine$sulphates, 0.05) +
  xlab('Sulphates'))
```

All the sulfur-related chemical content seems to have a positively skewed 
distribution. Summary of free sulfur dioxide, total sulfur dioxide and sulphates
in that order is below:
```{r echo=FALSE}
summary(redWine$free.sulfur.dioxide)
summary(redWine$total.sulfur.dioxide)
summary(redWine$sulphates)
```

Again, it can be seen that max value is much higher than the mean or 3rd
quartile, which is a typical characteristic of a long tail distribution with
some outliers. A log-log transformation is needed to be able to get a better look
of the distribution, except for sulphates since it has a tighter distribution.

```{r echo=FALSE}
grid.arrange(create_hist(redWine$free.sulfur.dioxide,0.2) +
  scale_x_continuous(trans='log10') + xlab('Log10 Free Sulfur Dioxide'), 
create_hist(redWine$total.sulfur.dioxide,0.1) +
  scale_x_continuous(trans='log10') + xlab('Log10 Total Sulfur Dioxide')) 
```

After taking the log10 transformation, we can see that the free sulfur dioxide,
total sulfur dioxide and sulfates and it looks like a normal distribution.  
Sulfur related component are added to wine to prevent bacterial growth but too
much sulfur dioxide will influence thesmell and taste of wine. 
Again, I decided to keep all the outliers with the same reasoning previously.
Now, let's look at the remaining components of wine.

```{r echo=FALSE}
grid.arrange(create_hist(redWine$chlorides, 0.01) +
  xlab('Chlorides'), 
create_hist(redWine$residual.sugar, 0.5) +
  xlab('Residual Sugar'), 
create_hist(redWine$alcohol, 0.5) +
  xlab('Alcohol'))
```

The chlorides and residual sugar follow a tight normal distribution with some 
outliers while the alcohol seems to have a longer tail and more positively 
skewed.

I am interested to look at the outliers for both chlorides and residual sugar
```{r echo=FALSE}
grid.arrange(ggplot(aes(x = 1, y = residual.sugar), data = redWine) + 
               geom_jitter(alpha = 0.1) +
               geom_boxplot(alpha = 0.2, color = 'red'),
              ggplot(aes(x = 1, y = chlorides), data = redWine) + 
               geom_jitter(alpha = 0.1) +
               geom_boxplot(alpha = 0.2, color = 'red'))
```
There are a considerable amount of outliers shown in the box plot but with the
same reasoning, I am going to keep all the outliers for analysis.
Lastly, we are going to look at the pH and density distribution.

```{r echo=FALSE}
grid.arrange(create_hist(redWine$pH, 0.05) +
  xlab('pH'), 
create_hist(redWine$density, 0.001) +
  xlab('density'))
```

All the wines are acidic with most of them having pH of 3-3.5. The density 
distribution of the wine is very tight and probably very dependent on the
alcohol content of the wine. The only way that density is more than water is
if the alcohol contains a lot of solids dissolved.

Let us begin to take subset of the wine data set and see the quality. 

```{r echo=FALSE}
#High volatile acid is when it is greater than 0.64 g/dm3 (3rd quartile)
ggplot(aes(quality),data = subset(redWine, redWine$volatile.acidity > 0.64)) +
  geom_bar() +
  scale_x_continuous() +
  ggtitle('Quality of High Volatile Acid Red Wine')
```

For higher volatility acid, it seems that it does not affect the quality of wine
as significantly since there is still a range of distribution but there seems to
be much more of quality 5 than 6 compared to when plotting the whole data set.

```{r echo=FALSE}
#High citric acid is when it is greater than 0.42 g/dm3 (3rd quartile)
ggplot(aes(quality),data = subset(redWine,citric.acid > 0.42)) +
  geom_bar() +
  scale_x_continuous() +
  ggtitle('Quality of High Citric Acid Red Wine')
```

Seems like higher citric acid content results in higher quality red wine as 
there are more higher quality ones compared to as a whole.

```{r echo=FALSE}
#High free sulfur dioxide is when it is greater than 50 g/dm3 when it starts to smell
ggplot(aes(quality),data = subset(redWine,free.sulfur.dioxide > 50))+
  geom_bar() +
  scale_x_continuous() +
  ggtitle('Quality of High Free Sulfur Dioxide Red Wine')
```

Surprisingly, it is not as bad as I expected it to be as usually sulfur smell 
and starts to become apparent over 50 ppm.

Last thing, I want to create a new variable to transform the wine quality into
categorical group with 0-4 as bad, 5-6 as average and 7-10 as good.

```{r echo=FALSE}
redWine$ratings <- ifelse(redWine$quality > 6, 'Good', 
                          ifelse(redWine$quality > 4, 'Average', 'Bad'))
redWine$ratings <- ordered(redWine$ratings, levels = c('Bad','Average','Good'))
ggplot(aes(ratings),data = redWine) +
  geom_histogram(stat = 'count') +
  xlab('Ratings')
```

Most wines are average rated by the wine experts. There are more good wine than
bad wine.

# Univariate Analysis


### What is the structure of your dataset?
My dataset contains 1599 observation with 11 different features that influences
the quality of the wine. There are 10 features (citric acid, free sulfur dioxide
, pH, fixed acidity, residual sugar, total sulfur dioxide. sulphates, volatile
acidity, chlorides and alcohol) that describes the chemical content and 1 
(density) that describes the physical property.

Quality is an ordered factor ranging from 0 (worst) to 10 (best)

Some observations:
- Most red wines are either quality 5 or 6.
- Most of the chemical components have a normal distribution except for the 
sulfur related ones and alcohol that has more of a positive skewed distribution
- There are a considerable amount of red wine that has no citric acid content
(around 10%)
- The density and pH of alcohol follow a pretty tight distribution with most pH 
between 3-3.5 and most density between 0.992 g/cm3 to 1.002 g/cm3.



### What is/are the main feature(s) of interest in your dataset?
The main feature of this dataset is the quality of the red wine judged by 
experts and how this different chemical components influences the rating
given by these experts. My guess is there are certain thresholds of each 
components that results in a better quality of wine. 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

Acidity, alcohol content, sulfur related components content and chlorides seems
to be components that have a strong effect on how red wine will taste and smell
which is strongly related to the quality of the dataset.

### Did you create any new variables from existing variables in the dataset?
Yes, I created an ordered rating for the quality of wine with 0-4 as Bad, 5-6 as
Average and 7-10 as Good.


### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

As I have mentioned before, most of the cheical components and density follows
a normal distribution. But interestingly, citric acid, alcohol and sulfur 
related components have a more positively skewed distribution. In order to 
know more about the distribution, I performed a log10 transformation to
understand the distribution more and the log10 transformation follows a normal
distribution.

# Bivariate Plots Section

```{r echo=FALSE}
newredWine <- redWine
newredWine$X <- NULL
newredWine$quality <- as.numeric(newredWine$quality)
newredWine$ratings <- NULL
RW <- cor(newredWine)
corrplot(RW,method="number")
```

From the plot, there are several variables that seems to be correlated.
1. Fixed acidity seems to correlate with citric acid, density and pH
2. For quality, alcohol, volatile acidity, citric acid and sulphate seems to 
have some correlation.
3. Some correlation between density and alcohol content

since we are interested mainly on red wine quality, let us look at the variables
that seems to have some correlation with red wine.


```{r echo=FALSE}
#create function to plot scatter between two variables
create_scatt <- function(x,y) {
  return(ggplot(aes(x = x, y = y), data = redWine) + 
           geom_point(position = 'jitter',alpha = 1/5) +
          geom_boxplot( alpha = .5,color = 'blue') + 
           stat_summary(fun.y = "mean", geom = "point", 
               color = "red", shape = 8, size = 4))
  }
```

```{r echo=FALSE}
create_scatt(factor(redWine$quality),redWine$alcohol) +
  xlab('Quality') +
  ylab('Alcohol')
```

There seems to be some positive relationship between alcohol content and 
quality. The box plot means help guide the eye to see the positive trend. 
From the correlation plot, R2 is 0.48. Quite expected as higher alcohol content
might imply that the wine was made from better quality grapes.

```{r echo=FALSE}
create_scatt(factor(redWine$quality),redWine$citric.acid) +
  xlab('Quality') +
  ylab('Citric Acid') 
```

There seems to be some positive relationship between alcohol content and 
quality. Again, the box plot means help guide the eye to see the positive trend. 
From the correlation plot, R2 is 0.23. Expected, as citric acid adds freshness
that adds to the quality of the red wine.

```{r echo=FALSE}
create_scatt(factor(redWine$quality),redWine$sulphates) +
  xlab('Quality') +
  ylab('Sulphates')
```

Slight positive trend can be seen between sulphates concentration and quality 
with R2 of 0.25. Interesting correlation plot shows trend with sulphates but not
free sulfur dioxide or total sulfur dioxide which serves as similar purpose.
Sulphates might also contribute to flavor.

```{r echo=FALSE}
create_scatt(factor(redWine$quality), redWine$volatile.acidity) +
  xlab('Quality') +
  ylab('Volatile Acid')
```

There seems to be a negative relationship between volatile acid concentration
and the quality of the red wine, with R2 of -0.39. Expected as volatile acid
is mainly consist of acetic acid that adds vinegary taste to red wine.

Looking at the plots above, there seems to be some trend even though there is 
a lot of scatter.

Let's look at other features to see if they have any correlation with each 
other.

```{r echo=FALSE}
ggplot(aes(x = alcohol, y = density), data = redWine) +
  geom_point(position = 'jitter', alpha = 1/5)
```

The higher the alcohol content, the lower the density. This makes sense since 
alcohol is less dense than water (majority of wine) and most of other components
of the wine.

The total acid in the wine is defined as the sum of fixed acidity, volatile 
acidity and citric acid. Let's make some plots with total acid. 

```{r echo=FALSE}
ggplot(aes(x = fixed.acidity + volatile.acidity + 
             citric.acid, y = pH), data = redWine) +
  geom_point(position = 'jitter', alpha = 1/5) +
  scale_x_continuous() +
  xlab('Total Acidity')

ggplot(aes(x = log10(fixed.acidity + volatile.acidity + 
                       citric.acid), y = pH), data = redWine) +
  geom_point(position = 'jitter', alpha = 1/5) +
  scale_x_continuous() +
  xlab('Log10 Total Acidity')
```

By definition, pH is the -log10 of H+ ions concentration and H+ ions are 
produced by acid so this plot makes sense.

Now let's look at the variables in regards to the red wine ratings using box 
plots.

```{r echo=FALSE}
#create function to plot box plot between two variables
create_box <- function(x,y) {
  return(ggplot(aes(x = x, y = y), data = redWine) + 
           geom_boxplot())
  }
```

```{r echo=FALSE}
create_box(redWine$ratings, redWine$volatile.acidity) +
  xlab('Ratings') +
  ylab('Volatile Acid')
create_box(redWine$ratings, redWine$citric.acid) +
  xlab('Ratings') +
  ylab('Citric Acid')
create_box(redWine$ratings, redWine$alcohol) +
  xlab('Ratings') +
  ylab('Alcohol')
create_box(redWine$ratings, redWine$sulphates) +
  xlab('Ratings') +
  ylab('Sulphates')
```

Great! The box plot supports the initial correlations that we see from the 
scatter plot. As we can see, Good wine has high sulphates, citric aid, alcohol
and has low volatile acidity.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

The feature of interest is the quality of red wine. Looking at the correlations, 
alcohol, citric acid and sulphates have a positive correlation with quality of 
alcohol while volatile acid has a negative correlation with red wine quality.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

The density of red wine is influenced by the alchohol content of the red wine 
while the pH is influenced by the acid content (because that is what pH is 
by definition)

### What was the strongest relationship you found?

The strongest relationship for red wine quality is alcohol content. 

# Multivariate Plots Section

From the previous analysis, we know what variables affect the quality of the red
wine. I will plot all combinations of the variables againsst quality and facet
with them ratings, hopefully by doing this we can capture any special 
interaction between these variables for the quality of redwine.

```{r echo=FALSE}
#create function to plot scatter plot between multivariables with ratings as
#facet
create_multi_facet_plot <- function(x,y) {
  return(ggplot(data = redWine,aes(x = x, y = y,
           color = factor(quality))) +
          geom_jitter() +
          scale_color_brewer(type='seq',
                   guide=guide_legend(title='Quality')) + 
          facet_wrap(~ratings))
}
```

```{r echo=FALSE, Multivariate_Plots}
create_multi_facet_plot(redWine$citric.acid, redWine$volatile.acidity) +
  xlab('Citric Acid') +
  ylab('Volatile Acid') 
```

We can see that in general that red wines with low citric acid has higher 
volatile acid compared to red wines that has high citric acid. But it is hard to
see if they have any effect of quality since the trend is similar for the three
ratings and the points are very spread out.

```{r echo=FALSE}
create_multi_facet_plot(redWine$alcohol, redWine$sulphates) +
  xlab('Alcohol') +
  ylab('Sulphates')
```

There seems to be no trend between alcohol and sulphates since all the points 
spreads out evenly across the ratings and it is hard to see if there is any 
trend in quality due to the variance of the points.

```{r echo=FALSE}
create_multi_facet_plot(redWine$alcohol, redWine$volatile.acidity) +
  xlab('Alcohol') +
  ylab('Volatile Acid')
```

In general, red wines with low alcohol content has higher volatile acid compared
to red wines that has high alcohol content. But again, it is hard to see if they
have any effect of quality since the trend is similar for the three ratings and
the points are very spread out.

```{r echo=FALSE}
create_multi_facet_plot(redWine$sulphates, 
                        redWine$volatile.acidity) +
  xlab('Sulphates') +
  ylab('Volatile Acid')
```

Similarly, it seems that red wines with low sulphates has higher volatile acid 
compared to red wines that has high sulphates and it is hard to see if they have
any effect of quality since the trend is similar for the three ratings.

```{r echo=FALSE}
create_multi_facet_plot(redWine$citric.acid, redWine$alcohol) +
  xlab('Citric Acid') +
  ylab('Alcohol')
```

No clear trend between citric acid and alcohol and it is hard to draw any
conclusions on quality as the points are highly spread out across the three 
ratings.

```{r echo=FALSE}
create_multi_facet_plot(redWine$sulphates, 
                        redWine$citric.acid) +
  xlab('Sulphates') +
  ylab('Citric Acid')
```

Again, it seems like the points are spread out and there is no trend between
citric acid and sulphates. Also hard to see any trend with quality since the 
variance is present across the ratings.

It seems like we need to remove the ratings facet and add linear models to 
visualize the trends in quality between the variables better.

```{r echo=FALSE}
#create function to plot scatter plot between multivariables
create_multi_jitter_plot <- function(x,y) {
  return(ggplot(data = redWine,aes(x = x, y = y,
           color = factor(quality))) +
          geom_point(alpha = 0.8, size = 1) +
          geom_smooth(method = "lm", se = FALSE,size=1)  +
          scale_color_brewer(type='seq',
                   guide=guide_legend(title='Quality')))
  }
```

```{r echo=FALSE}
create_multi_jitter_plot(redWine$citric.acid, redWine$volatile.acidity) +
  xlab('Citric Acid') +
  ylab('Volatile Acid') 
```

The linear model confirms what we see above, volatile acid content in red wine
decreases with increasing citric acid. But we can also see that lower quality
red wines has higher volatile acid content compared to higher quality red wines.
```{r echo=FALSE}
create_multi_jitter_plot(redWine$alcohol, redWine$sulphates) +
  xlab('Alcohol') +
  ylab('Sulphates')
```
Flatness of the linear model across all quality of red wines implies that the 
amount of alcohol and sulphates does not correlate. But we can see that higher
quality red wine has higher sulphates across all concentration of alcohol.

```{r echo=FALSE}
create_multi_jitter_plot(redWine$volatile.acidity, redWine$alcohol) +
  xlab('Volatile Acid') +
  ylab('Alcohol')
```

For quality 3 and 8, there seems to be higher volatile acid for higher alcohol
content, but the rest seems to show that there is no relationship between amount
of alcohol and volatile acid. It can be seen that higher alcohol content results
in higher quality of red wine.

```{r echo=FALSE}
create_multi_jitter_plot(redWine$sulphates, 
                         redWine$volatile.acidity) +
  xlab('Sulphates') +
  ylab('Volatile Acid')
```

Lower quality alcohols has higher volatile acid content. There seems to be
some relationship between sulphates and voltaile acid concentration where
the higher the sulphates, the lower the volatile acid concentration is and it is
especially true for red wine that has quality of 3.

```{r echo=FALSE}
create_multi_jitter_plot(redWine$alcohol, redWine$citric.acid) +
  xlab('Alcohol') +
  ylab('Citric Acid')
```

Generally, higher citric acid results in higher quality of red wine and there 
is no relationship between alcohol content and citric acid concentration. But,
it seems for red wine that has quality of 3 and 8, the higher alcohol content 
the lower the citric acid concentration. This relationship is expected looking 
at the previous graph (alcohol and volatile acid) and knowing that volatile
acid and citric acid has inverse relationship.


```{r echo=FALSE}
create_multi_jitter_plot(redWine$sulphates, 
                         redWine$citric.acid) +
  xlab('Sulphates') +
  ylab('Citric Acid')
```

There seems to be a positive relationship between citric acid content and 
sulphates in red wines. Higher sulphates seems to result in higher citric acid
and this relationship is more dramatic for red wine that has quality of 3.

Fitting linear models help to see the trend of the effect of the variables on 
the different qualities better. 

Let's look at the coefficient of the models on the variables that seems to have 
more effect on red wine quality. They are citric acid vs sulphates, volatile 
acid vs sulphates and alcohol vs sulphates shown below in that order.

```{r echo=FALSE}
fit1 <- lm(quality ~ citric.acid + sulphates, data = redWine)
summary(fit1)
fit2 <- lm(quality ~ volatile.acidity + sulphates, data = redWine)
summary(fit2)
fit3 <- lm(quality ~ alcohol +sulphates, data = redWine)
summary(fit3)
```

Alcohol and log10 sulphates seems to have the highest R-squared value when 
fitted to a linear model for the quality of red wine compared to other variables
that looked promising initially.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

After plotting all the variables that seems to have influence on quality with
each other, it seems there are certain combinations of variable that exhibits 
clearer trends on affecting the quality of red wine while others just seem to
have more of a spread.

### Were there any interesting or surprising interactions between features?
There were no surprising interaction between the features. Most of the results
are expected after plotting the bivariate graphs.


### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

Yes. I created linear model on a combination of 2 variables that looks pretty
promising from the scatter plot. Alcohol and log10 sulphates seems to have the
strongest correlation with the quality of red wine compared to others that I 
modelled
------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(quality),data=redWine) + geom_histogram(stat='count',binwidth=1) + ggtitle('Distribution of Quality of Red Wine') + xlab('Quality of Red Wine') +
  ylab('Count')
```

### Description One
This is the distribution of the quality of the red wines in the data set judged 
by experts. As you can see, most wines fall in the range of 5-6, while there 
are a few expectional ones and at the same time, a few poor quality ones. 
Interestingly, there are no red wine that is super good (quality close to 10) or
super bad (quality close to 0). Also, the quality of red wine is a whole number.
The distribution follows a normal distribution.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x = ratings, y = sulphates), data = redWine) +
  geom_boxplot() +
  xlab('Ratings') + 
  ylab('Sulphates (g/dm3)')
```

### Description Two
When you categorize the red wine quality into 3 groups: Bad (0-4), Average (5-6)
and Good (7-10) and plot it against several physiochemical properties such as
sulphates, citric acid content and alcohol content, you are able to see that 
it follows a certain trend. This plot shows quality plotted with sulphates.

In general, better quality wine has more citric acid, more alcohol, 
more sulphates and less volatile acid (acetic acid).

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(data = redWine,
       aes(y = log10(sulphates), x = alcohol, color = factor(quality))) +
  geom_jitter() +ylab('log10 Sulphates (g/dm3)') +
  xlab('Alcohol Content (% volume)') +
  ggtitle ('Quality Based on Sulphates and Alcohol Content') +
  scale_color_brewer(type='seq',
                   guide=guide_legend(title='Quality'))
```

### Description Three
I attempted to model the quality of red wines using two of the physiochemical
properties that seems to show the strongest correlation: alcohol and sulphates.
The R-squared coefficient of this model is 0.29 which is considerably low for
a linear model but the highest compared to other physiochemical properties.

------

# Reflection
The red wine data set contains 1599 observations of red wines with 11 variables
that describes the physical properties and chemical properties of the wine. The
quality of each red wine judged by experts is also included as one of the 
variable in the data set.
Initially, I looked at the distributions of the all the variables in the 
dataset, some of them exhibit normal distribution but many of them show 
positively skewed long tail distribution. Taking a log10 transformation 
to these distributions shows a normal looking distribution.

Using GGpairs function, I am able to see the correlation of all variables in a
glimpse and from there decided to choose pairs that seems to have slight
correlation. There are quite a few pairs that seems to have some correlation
so it is quite a struggle to choose which to focus on. Since the variable of 
interest is quality of the red wine I decided to spend more time looking at the
variables that has some correlation with the quality of the red wine. Also, by 
creating a new ratings variable that breaksdown the quality of red wine into 
three groups (Bad, Average and Good), it is easier to see the effect of each 
chemical properties that influences the quality of red wine. Next, I decided to
plot the quality of the red wine with two variables and see if there are any 
surprising changes but it seems like the trends are congruent with the bivariate
plots. Using a linear model, I tried to create a model for the quality of the 
red wine using two variables: alcohol content and sluphates content but due to 
the scatter of the data, I obtained a low R-squared value for the correlation.

I think the main problem is that the quality is in discrete whole numbers 
instead of a continuous number. For future improvement, using a more precise
number for quality (such as 5.56 instead of just 6) will result in better 
modelling curves and analysis since all the variables (physical and chemical 
properties) are continuous numbers. Also, I can try other models instead of 
linear to fit the data since the taste and quality of red wine is a result of 
complicated interactions between a variety of different chemical and physical 
properties inside the red wine and a simple linear model will not suffice.